%-------------------------
% Resume in Latex
% Author : Aryan Singh
%------------------------

\documentclass[a4paper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.4in}
\addtolength{\evensidemargin}{-0.4in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\parskip}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{\item\small{\textbf{#1:} #2 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{\vspace{-1pt}\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-5pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Aryan Singh} & Email: \href{mailto:singharyan4477@gmail.com}{singharyan4477@gmail.com}\\
  \href{https://www.linkedin.com/in/Aryan447}{linkedin.com/in/Aryan447} & Phone: +91-9713904100 \\
\end{tabular*}

%---------SUMMARY---------
\section{Professional Summary}
Results-oriented Machine Learning Engineer and Data Analyst experienced in data preprocessing, model design, and deployment of production-grade ML pipelines. Strong grasp of data analysis, feature engineering, and model optimization using Python, Scikit-learn, TensorFlow, and XGBoost. Skilled in SQL, cloud integration, REST API development, and performance tuning. Proficient in C/C++, Java, Go, and Linux-based systems. Strong in DSA and OOP, with proven ability to build scalable, reliable, and explainable solutions across AI-driven systems.

%-----------EXPERIENCE-----------------
\section{Work Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Cognifyz Technologies}{Remote}
    {Machine Learning Engineer Intern}{Feb 2025 -- Jul 2025}
    \resumeItemListStart
      \resumeItem{Model Development}
        {Designed ML models for restaurant rating prediction using Scikit-learn and Pandas; improved RMSE by 18\% with advanced feature engineering and scaling.}
      \resumeItem{Classification Pipeline}
        {Trained Logistic Regression, Random Forest, and XGBoost classifiers achieving 89\% accuracy via cross-validation and parameter optimization.}
      \resumeItem{Automation and Deployment}
        {Automated data preprocessing and model evaluation pipelines with REST API integration, reducing manual effort by 40\% and improving response time by 25\%.}
      \resumeItem{Collaboration and Workflow}
        {Applied Agile and version control using Git, JIRA, and CI/CD pipelines ensuring reproducible and efficient development cycles.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

  \resumeSubheading
    {Anti-Money Laundering Detection System}{}
    {Python, XGBoost, MEALPY, PSO, GWO, NumPy, Pandas, Matplotlib}{}
    \resumeItemListStart
      \resumeItem{Model Implementation}
        {Analyzed 32 million transactions of IBM AML dataset and developed fraud detection model with imbalance handling (SMOTE) and categorical encoding.}
      \resumeItem{Optimization Algorithms}
        {Enhanced XGBoost with PSO and GWO optimizers improving precision by 20\% and recall by 24\%.}
      \resumeItem{Explainability and Compliance}
        {Used SHAP and LIME for model interpretation ensuring transparency for financial compliance teams.}
      \resumeItem{Production Deployment}
        {Deployed the containerized model through Docker with REST endpoints for real-time prediction and monitoring.}
    \resumeItemListEnd

\resumeSubheading
  {Concurrent Chat Application}{}
  {Go, TCP/IP, Concurrency, Channels, Goroutines, Docker, Distributed Systems}{}
  \resumeItemListStart
    \resumeItem{Scalable Architecture}
      {Built concurrent chat server handling 200+ simultaneous client connections using goroutines, channels, and event-driven message broadcasting.}
    \resumeItem{Latency Optimization}
      {Reduced end-to-end message latency by 30\% through buffered channels, connection pooling, and efficient synchronization primitives.}
    \resumeItem{Fault Tolerance}
      {Implemented heartbeat checks and automatic reconnection flows achieving ~99.9\% uptime with graceful handling of dropped connections.}
    \resumeItem{Resource Efficiency}
      {Optimized CPU/memory consumption enabling stable multi-threaded performance on low-compute servers and edge-hosted environments.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Madhav Institute of Technology \& Science (MITS)}{Gwalior, MP}
    {B.Tech in Artificial Intelligence and Machine Learning | CGPA: 7.1/10}{Nov 2021 -- Jun 2025}
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
  \item{
    Programming: Python, C/C++, Java, Go, JavaScript/TypeScript, SQL, Bash \\
    ML & AI: TensorFlow, PyTorch, Scikit-learn, XGBoost, NumPy, Pandas, OpenCV, MEALPY \\
    Development: REST APIs, Flask, React, gRPC, WebSockets, Redis, Database Design, API Integration \\
    DevOps & Tools: Git, Docker, Linux, CI/CD, VSCode, Postman, JIRA, Cloud (AWS/GCP), Virtualization \\
    Concepts: Data Structures, Algorithms, OOP, System Design, OS, DBMS, CN, Data Preprocessing \\
    Additional: Data Visualization, Feature Selection, Model Monitoring, Optimization, Leadership, Teamwork
  }
\resumeSubHeadingListEnd

%-----------CERTIFICATIONS & ACHIEVEMENTS-----------
\section{Achievements and Certifications}
\resumeSubHeadingListStart
  \resumeItemListStart
    \resumeItem{Problem Solving}
      {Solved 200+ algorithmic problems on LeetCode, GFG, and CodeStudio demonstrating analytical reasoning.}
    \resumeItem{Certification}
      {Completed Blockchain and Its Applications (NPTEL, IIT Kharagpur) with verified certification.}
    \resumeItem{Research Publication}
      {Submitted research paper – Dual-Stage Predictive Model for ICU Risk Stratification, ICSISCET 2025, Springer LNCS (Scopus Indexed)}
    \resumeItem{Hackathons}
      {Ranked Top 10 among 80+ teams at MITS Hackathon 2024 for developing an AI-based decision automation tool.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
